Time Series Bootstrapping For Solar Current

### 2021-12-07 deliverables/paper.Rmd
Added initial comparison to normal bootstrap

hour_plot_of_var(df, "GHI")
hour_plot_of_var(df, "current_out")
hour_plot_of_var(df, "declination_angle")
hour_plot_of_var(df, "solar_time")
hour_plot_of_var(df, "angle_sun_surface_degrees")
```

@@

block_bootstrap_estimates_from_df <- function(df, B=10000) {
  block_bootstrap_estimates <- rep(NA, B)
  blocks <- make_blocks_from_df(df)
  number_of_blocks <- nrow(blocks)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:number_of_blocks, number_of_blocks, replace = TRUE)
    # Concatenate blocks at the given indices
    # This gives a "pseudo-dataset" containing resampled blocks
    block_bootstrap_estimates[i] <- mean(as.vector(t(blocks[idx, ])))
  }
  return(block_bootstrap_estimates)
}
test_est <- block_bootstrap_estimates_from_df(df_high_irradiance)

>>>>

hour_plot_of_var(df, "GHI")
hour_plot_of_var(df, "current_out")
```

@@

block_bootstrap_estimates_from_df <- function(df, B=10000) {
  block_bootstrap_estimates <- rep(NA, B)
  blocks <- make_blocks_from_df(df)
  number_of_blocks <- nrow(blocks)
  for (i in 1:B) {
    # sample blocks
    idx <- sample(1:number_of_blocks, number_of_blocks, replace = TRUE)
    # Concatenate blocks at the given indices
    # This gives a "pseudo-dataset" containing resampled blocks
    block_bootstrap_estimates[i] <- median(as.vector(t(blocks[idx, ])))
  }
  return(block_bootstrap_estimates)
}
test_est <- block_bootstrap_estimates_from_df(df_high_irradiance)

meanv <- function(data, idx) {
  return(mean(data[idx]))
}

sdv <- function(data, idx) {
  return(sd(data[idx]))
}

medianv <- function(data, idx) {
  return(median(data[idx]))
}

iid_bootstrap_estimates_from_df <- function(df, B=10000) {
  boot_current <- boot(df$current_out, medianv, B)
  return(boot_current$t)
}

test_iid <- iid_bootstrap_estimates_from_df(df_high_irradiance)

ggplot() +
  geom_histogram(aes(x = test_est),color="red",alpha=0.5) +
  geom_histogram(aes(x = test_iid),color="blue",alpha=0.5) +
  theme_bw()
